# Methods


<!-- ```{r setup, include=FALSE} -->
<!-- knitr::opts_chunk$set(echo = TRUE) 
eval = TRUE, echo = TRUE, results = "hide"
-->
<!-- ``` -->

```{r setup, eval = TRUE, echo = FALSE, include=TRUE}
library(DiagrammeR)
mermaid("graph TD
A[Aprendizado de máquinas] --> B[Aprendizados]
B-->C[supervisionado]
B-->D[por reforço]
B-->E[Não supervisionado]
C-->F[classificação]
C-->G[Regressão]
E-->H[Clustering]
E-->I[Redução de dimensionalidade]")
```

```{r}
DiagrammeR::grViz("digraph {
  graph [layout = dot, rankdir = TB]
  
  node [shape = rectangle]        
  rec1 [label = 'Step 1. Wake up']
  rec2 [label = 'Step 2. Write code']
  rec3 [label =  'Step 3. ???']
  rec4 [label = 'Step 4. PROFIT']
  
  # edge definitions with the node IDs
  rec1 -> rec2 -> rec3 -> rec4
  }", 
  height = 500)
```


Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

We describe our methods in this chapter.

block
```{block, type='NOTA'}
Some text for this block.
```



::: {.infobox .obra data-latex="{construcao}"}
_EM CONSTRUÇÃO_
:::

::: {.infobox .note data-latex="{note}"}
**NOTICE!**

Thank you for noticing this **new notice**! Your noticing it has
been noted, and _will be reported to the authorities_!
:::


::: {.infobox .history data-latex="{history}"}
**NOTICE!**

Thank you for noticing this **new notice**! Your noticing it has
been noted, and _will be reported to the authorities_!
:::

block2
```{block2, type='FOO'}
Some text for this block [@citation-key].

- a list item
- another item

More text.
```



## Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```